Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-03-14 paper/snakemajoranas.tex
remove old figure
use symbols in the abstract

\date{\today}
\begin{abstract}
High density superconductor-semiconductor-superconductor junctions have a small induced superconducting gap due to the quasiparticle trajectories with a large momentum parallel to the junction having a very long flight time.
Because a large induced gap protects Majorana modes, these long trajectories constrain Majorana devices to a low electron density.
We show that a zigzag-shaped geometry eliminates these trajectories, allowing the robust creation of Majorana states with both the induced gap and the Majorana size improved by more than an order of magnitude for realistic parameters.
In addition to the improved robustness of Majoranas, this new zigzag geometry is insensitive to the geometric details and the device tuning.
\end{abstract}

>>>>

\date{\today}
\begin{abstract}
High density superconductor-semiconductor-superconductor junctions have a small induced superconducting gap due to the quasiparticle trajectories with a large momentum parallel to the junction having a very long flight time.
Because a large induced gap protects Majorana modes, these long trajectories constrain Majorana devices to a low electron density.
We show that a zigzag-shaped geometry eliminates these trajectories, allowing the robust creation of Majorana states with both the induced gap $E_\textrm{gap}$ and the Majorana size $\xi_\textrm{M}$ improved by more than an order of magnitude for realistic parameters.
In addition to the improved robustness of Majoranas, this new zigzag geometry is insensitive to the geometric details and the device tuning.
\end{abstract}
